### 2018-01-18 dissemination.publication/request-overview-sysml2018/paper.tex
fixed repo after mix up

\documentclass[10pt,letterpaper,twocolumn]{article}

\usepackage[margin=2cm]{geometry}

\special{papersize=8.3in,11.7in} % A4

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\usepackage{multicol}
%\usepackage{ifpdf}
%\usepackage{cite}
\usepackage{graphicx}
\usepackage{array}
%\usepackage{caption}
\usepackage{subfig}
%\usepackage{subfigure}
%\usepackage{fixltx2e}
\usepackage{algorithm,algorithmic}
\usepackage{color}
%\usepackage[hyphens]{url}
\usepackage{url}
\usepackage{hyperref}
\usepackage{listings}
\usepackage[none]{hyphenat}

\newenvironment{packed_itemize}{
\begin{itemize}
  \setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}
}{\end{itemize}}

\renewcommand{\floatpagefraction}{.8}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\title{Introducing ReQuEST: an Open Platform for Reproducible\\and Quality-Efficient Systems-ML Tournaments}

\author{Thierry Moreau$^{1}$, Anton Lokhmotov$^{2}$, Grigori Fursin$^{3}$ \\
\\
$^1$~University of Washington, USA ; $^2$~dividiti, UK ; $^3$~cTuning foundation, France\\
}

\date{December, 2017}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\author{Thierry Moreau}
%\affiliation{\institution{University of Washington, USA}}

%\author{Anton Lokhmotov}
%\affiliation{\institution{dividiti, UK}}

%\author{Grigori Fursin}
%\affiliation{\institution{cTuning foundation, France}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\maketitle

\begin{abstract}
 \input{paper_abstract}
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%CK_INTERACTIVE_START

%CK_ABSTRACT={paper_abstract.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction} % Has to be here (for interactive report!)
\label{introduction} % Has to be here (for interactive report!)

   %CK={"action":"prepare_for_latex", "cid":"slide:8e550a5184760aab", "file":"b4b07ad3a7839327-cropped.pdf", "path":"ck-assets", "ck_image":"yes", "ck_image_width":600}
   \begin{figure*}[t]
     \centering
      \includegraphics[width=4.9in]
      {ck-assets/b4b07ad3a7839327-cropped.pdf} %CK_URL={b4b07ad3a7839327-cropped.pdf}
     \caption{
       Collective Knowledge framework as an open platform to support open tournaments 
       for software/hardware co-design of Pareto-efficient deep learning
       and other emerging workloads in terms of speed, accuracy, energy and various costs.
     }
     \vspace{-1em}
     \label{fig:reproducible-tournaments}
   \end{figure*}

Machine learning has undergone a rapid pace of progress 
over the recent years. Rarely in the scientific community have
we witnessed such a concerted effort from various communities
(machine learning, systems, hardware, security, programming
languages etc.) in improving the performance, accuracy,
robustness and cost of machine learning based systems.

However, implementing such systems for a given problem 
(for example, deep learning algorithm for ImageNet classification), 
one has to navigate a multitude of design decisions: 
what network architecture to deploy and how to customize it (ResNet vs.\ MobileNet), 
what framework to use (MXNet vs. TensorFlow), 
what libraries and which optimizations to employ (MKL vs.\ OpenBLAS),
which is generally a consequence of the target
hardware platform (Intel Xeon + NVIDIA GPU vs.\ ARM-based mobile SoC). 
%
On top of these implementation decisions,
platform-specific decisions may affect the performance and
overall experience in deploying the system in question:
details such as operating system, kernel version, framework
and library versions or dependencies, and custom optimizations.
%
As a result a given system implementation (for example, ResNet
on TensorFlow on a Intel + NVIDIA hardware system) can have
many incarnations, some of which may have drastically
different performance results. 
%
Furthermore, as more papers are being published, it also becomes 
challenging to reproduce, reuse, build on top of, and perform 
fair comparisons of numerous machine learning techniques 
across rapidly evolving systems.

As multiple communities tackle the same challenges 
of making machine learning systems 
faster, cheaper, smaller, more accurate, and more energy efficient 
across diverse platforms from IoT to data centers, 
we need a platform to automate and perform apples-to-apples comparisons 
of different approaches that aim to achieve the same goal. 
%
For example, how does an approximate analog accelerator
for deep learning compare to algorithmic simplifications
on off-the-shelf hardware in terms of accuracy vs.\ efficiency
Pareto optimality?

We therefore propose the Reproducible Quality-Efficient Systems
Tournament (ReQuEST) as a community-driven platform 
for reproducible, comparable, and multi-objective 
optimization of emerging workloads
% suggested by an industrial board
~\cite{request}.
%
We plan to host ReQuEST as a bi-annual workshop alternating
between systems and machine learning communities.
%
Its first incarnation will take place at ASPLOS in March 2018
and will focus solely on optimizing inference on real systems 
to test our platform and use the feedback from participants and
an industrial board
to improve it.

We detail in the next sections how its objectives and
execution differentiate ReQuEST from other existing workshop-based
competitions.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Main goals}

\textbf{Summary:} ReQuEST is aimed at providing a scalable tournament framework, 
a common experimental methodology and an open repository for continuous evaluation 
and optimization of the quality vs.\ efficiency Pareto optimality of a wide range 
of real-world applications, libraries, and models across the whole 
hardware/software stack on complete platforms as conceptually shown 
in Figure~\ref{fig:reproducible-tournaments}.

\textbf{Tournament framework goals:} we want to promote reproducibility 
of experimental results and reusability/customization of systems research artifacts 
by standardizing evaluation methodologies and facilitating the deployment 
of efficient solutions on heterogeneous platforms. 
%
For that reason, packaging artifacts and experimental results requires a bit more
involvement than sharing some CSV files or checking out a given GitHub repository. 
%
   %CK={"action":"prepare_for_latex", "cid":"slide:04ac48e744b30ba6", "file":"32c0b60dcc114aa8-cropped.pdf", "path":"ck-assets", "ck_image":"yes", "ck_image_width":800}
   \begin{figure*}[!htbp]
     \centering
      \includegraphics[width=5.2in]
      {ck-assets/32c0b60dcc114aa8-cropped.pdf} %CK_URL={32c0b60dcc114aa8-cropped.pdf}
     %CK_INTERACTIVE_GRAPH_PASSIVE={"cid":"2d41f89bcf32d4d4:f99f35d22d6424e9", "where":"div#ck_interactive_35cecc1de4b9ba60", "html":"interactive.html", "style":"interactive.style", "add_div":"yes", "add_box":"yes", "box_width":800, "remove_script_src":"yes", "remove_script_src":"no"}
     \caption{
      An example of a live Collective Knowledge scoreboard to crowd-benchmark
      inference in terms of speed and platform cost 
      across diverse deep learning frameworks, models, data sets, and 
      Android devices provided by volunteers. Red dots 
      are associated with the winning workflows (model/software/hardware).
     }
     \vspace{-1em}
     \label{fig:dnn-crowdtuning-example}
   \end{figure*}

That is why we build our competition on top of an open-source 
and portable workflow framework (Collective Knowledge or CK~\cite{ck-date16})
and a standard ACM artifact evaluation methodology~\cite{ctuning-ae} 
from premier ACM systems conferences (CGO, PPoPP, PACT, SuperComputing) 
to provide unified evaluation and a live scoreboard of submissions
as demonstrated in Figure~\ref{fig:dnn-crowdtuning-example}.

CK is a Python wrapper framework to share artifacts and workflows 
as customizable and reusable plugins with a common JSON API and meta description,
and adaptable to a user platform with Linux, Windows, MacOS and Android.
%
For example, it has already been used and extended in a number of academic and industrial projects
to automate and crowdsource benchmarking and multi-objective optimization of deep learning
across diverse platforms, environments, and data sets.
%
Figure~\ref{fig:dnn-crowdtuning-example} shows a proof-of-concept example of a live scoreboard 
powered by CK to collaboratively benchmark inference (speed vs.\ platform cost) 
across diverse deep learning frameworks (TensorFlow, Caffe, MXNet, etc.), 
models (AlexNet, GoogleNet, SqueezeNet, ResNet, etc.), real user data sets, and mobile devices 
provided by volunteers (see the latest results at \href{http://cknowledge.org/repo}{cKnowledge.org/repo}).

\textbf{Metrics and Pareto-optimality goals:} we want to stress
quality-awareness to the architecture/compilers/systems community,
and resource-awareness to the applications/algorithms community and
end-users. The submissions and their evaluation metrics will
be maintained in a public repository that includes a live
scoreboard.

Specific attention will be brought to submissions 
close to a Pareto frontier in a multi-dimensional 
space of accuracy, execution time, power/energy consumption, 
hardware/code/model footprint, monetary costs etc.

\textbf{Application goals:} in the long term, we will
cover a comprehensive suite of workloads, datasets and models
covering applications domains that are most relevant
to machine learning and systems researchers. 
This suite will continue evolving according 
to feedback and contributions from the academia and industry.
All artifacts from this suite can be automatically plugged 
in to the ReQuEST competition workflows to simplify and automate 
experimentation.

\textbf{Complete platforms goals:} we aim to cover
a comprehensive set of hardware systems from data-centers down
to sensory nodes, incorporating various forms of processors
including GPUs, DSPs, FPGAs, neuromorphic and even analogue
accelerators in the long term.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Future work}

Our goal is to bring multi-disciplinary researchers to 
\begin{enumerate}
  \item release research artifacts of their on-going or accomplished research,
standardize evaluation workflows, and facilitate deployment
and tech transfer of state-of-the-art research,
  \item foster exploration of quality-efficiency trade-offs, and 
  \item create a discussion ground to steer the community towards new
applications, frameworks, and hardware platforms.
\end{enumerate}

We want to set a coherent research roadmap for
researchers by hosting bi-annual tournaments complemented with
panel discussions from both academia and industry. We hope
that as participation increases, the coverage of problems
(vision, speech and even beyond machine learning) and
platforms (novel hardware accelerators, SoCs, and even exotic
hardware such as analog, neuromorphic, stochasticm, quantum) will increase.

ReQuEST is organized as a bi-annual workshop, alternating
between systems-oriented and machine learning-oriented
conferences. The first ReQuEST workshop will be co-located
with ASPLOS in March 2018. The workshop will aim to present
artifacts submitted by participants, along with
a multi-objective scoreboard, where quality-efficient
implementations will be rewarded. 
The submissions will be validated by an artifact evaluation committee, 
and participants will have the chance to get an artifact paper
published as ACM proceedings.

In addition we wish to nurture
a discussion ground for artifact evaluation in multidisciplinary
research, gathering perspectives from machine learning,
systems, compilers and architecture experts. 
%
We will use this discussion to continuously improve and extend 
functionality of our tournament platform.
%
For example, we plan to gradually standardize the API and meta description of all artifacts 
and machine learning workflows with the help of the community, 
provide architectural simulators and simulator-based evaluations, 
cover low-level optimizations, expose more metrics, and so on.

Finally, an industrial panel composed of research-representatives from
prominent software and hardware companies will discuss how
tech-transfer can be facilitated between academia and
industry, and will help craft the roadmap for the ReQuEST
workshops by suggesting new datasets, workloads, metrics, and
hardware platforms.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bibliographystyle{abbrv}
\bibliography{paper}

\end{document}

### 2018-01-18 dissemination.publication/request-overview-sysml2018/paper_abstract.tex
fixed repo after mix up

Co-designing efficient machine learning based systems across
the whole hardware/software stack to trade off speed, accuracy, energy
and costs is becoming extremely complex and time consuming.
%
Researchers often struggle to evaluate and compare different
published works across rapidly evolving software
frameworks, heterogeneous hardware platforms, compilers,
libraries, algorithms, data sets, models, and environments.

We~\footnote{ReQuEST organizers (A-Z): 
Luis Ceze, University of Washington (USA),
Natalie Enright Jerger (University of Toronto, Canada),
Babak Falsafi (EPFL, Switzerland),
Grigori Fursin, (cTuning foundation, France),
Anton Lokhmotov, (dividiti, UK),
Thierry Moreau, (University of Washington, USA),
Adrian Sampson, (Cornell University, USA)
Phillip Stanley Marbell, (University of Cambridge, UK)}
present our community effort to develop an open co-design tournament 
platform with an online public scoreboard.
%
It will gradually incorporate best research practices 
while providing a common way for multidisciplinary researchers
to optimize and compare the quality vs. efficiency Pareto
optimality of various workloads on diverse and complete
hardware/software systems.
%
We want to leverage the open-source Collective Knowledge framework
and the ACM artifact evaluation methodology to validate and share the complete 
machine learning system implementations
in a standardized, portable, and reproducible fashion.
%
We plan to hold regular multi-objective optimization and co-design tournaments 
for emerging workloads such as deep learning, starting with ASPLOS'18 
to build a public repository of the most efficient algorithms and systems
which can be easily reused and built upon.
%
We will also use the feedback from participants to continue improving
our platform and common co-design methodology.

### 2018-01-18 wfe/request/request-template.tex
fixed repo after mix up

% LaTeX template for Artifact Evaluation V20170622
%
% Prepared by Grigori Fursin (cTuning foundation, France and dividiti, UK),
% Bruce Childers (University of Pittsburgh, USA),
% Thierry Moreau (University of Washington, USA)
%
% See example of this Artifact Appendix in the CGO'17 paper (with the CK workflow framework):
% https://www.cl.cam.ac.uk/~sa614/papers/Software-Prefetching-CGO2017.pdf
%
% (C)opyright 2014-2017
%
% CC BY 4.0 license
%

\documentclass{sigplanconf}

\begin{document}

\special{papersize=8.5in,11in}

\title{Title}

\authorinfo{John Doe}
{Affiliation}
{johndoe@email.com}

\maketitle

\begin{abstract}
Summary of work, and artifact.
\end{abstract}

\section{Extended Abstract}

\subsection{Technical Description}
{\em Obligatory. Provide a technical desciption of your novel work, or references to
your already published work which you are providing an artifact for.}

\subsection{Empirical Evaluation}
{\em Obligatory. Provide empirical evaluation results of the technique together with improved metrics, 
optimization, or exploration which you are providing an artifact for, and discuss the insights 
that the evaluation provides. The methodology can be discussed in more details in the artifact appendix.}

\newpage

\appendix
\section{Artifact appendix}

Submission and reviewing guidelines and methodology: \\
{\em http://cTuning.org/ae/submission.html}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Abstract}

{\em Obligatory}

\subsection{Artifact check-list (meta-information)}

{\em Obligatory. Use just a few informal keywords in all fields applicable to your artifacts
and remove the rest. This information is needed to find appropriate reviewers and gradually 
unify artifact meta information in Digital Libraries.}

{\small
\begin{itemize}
  \item {\bf Algorithm: }
  \item {\bf Program: }
  \item {\bf Compilation: }
  \item {\bf Transformations: }
  \item {\bf Binary: }
  \item {\bf Data set: }
  \item {\bf Run-time environment: }
  \item {\bf Hardware: }
  \item {\bf Run-time state: }
  \item {\bf Execution: }
  \item {\bf Metrics: }
  \item {\bf Output: }
  \item {\bf Experiments: }
  \item {\bf Workflow frameworks used?: }
  \item {\bf Publicly available?: }
\end{itemize}

{\em Obligatory. Provide brief assessment of your artifacts 
based on {\em https://www.acm.org/publications/policies/artifact-review-badging}}:

\begin{itemize}
  \item {\bf Artifacts publicly available?: }
  \item {\bf Artifacts functional?:}
  \item {\bf Artifacts reusable?:}
  \item {\bf Results validated?:}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Description}

\subsubsection{How delivered}

{\em Obligatory}

\subsubsection{Hardware dependencies}

\subsubsection{Software dependencies}

\subsubsection{Data sets}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Installation}

{\em Obligatory}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Experiment workflow}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Evaluation and expected result}

{\em Obligatory}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Experiment customization}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Notes}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% When adding this appendix to your paper, 
% please remove below part
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}

### 2018-01-18 dissemination.publication/request-overview-sysml2018/_generate_interactive_ck_article.sh

@@ -1,0 +1,9 @@
+# generate bbl in the format understandable by CK
+ck replace_string_in_file fgg.misc --file=paper.tex --string=ACM-Reference-Format --replacement=abbrv
+
+pdflatex paper
+bibtex paper
+
+ck convert_to_live_ck_report # --output=interactive-ck-article.html
+
+ck replace_string_in_file fgg.misc --file=paper.tex --string=abbrv --replacement=ACM-Reference-Format

### 2018-01-18 module/request/module.py

@@ -1,0 +1,1714 @@
+#
+# Collective Knowledge: CK-powered AI/SW/HW co-design for ReQuEST tournaments
+#
+# See CK LICENSE.txt for licensing details
+# See CK COPYRIGHT.txt for copyright details
+#
+# Developer: Grigori Fursin, cTuning foundation/dividiti
+#
+
+cfg={}  # Will be updated by CK (meta description of this module)
+work={} # Will be updated by CK (temporal data)
+ck=None # Will be updated by CK (initialized CK kernel) 
+
+# Local settings
+
+line='================================================================'
+
+ck_url='http://cknowledge.org/repo/web.php?native_action=show&native_module_uoa=program.optimization&scenario=a555738be4b65860'
+ck_url1='http://cknowledge.org/repo/web.php?wcid=request:'
+
+ffstat='ck-stat-flat-characteristics.json'
+ffmin='ck-stat-flat-min.json'
+
+form_name='wa_web_form'
+onchange='document.'+form_name+'.submit();'
+
+hextra='<i><center>\n'
+hextra+='</center></i>\n'
+hextra+='<br>\n'
+
+selector=[{'name':'Type', 'key':'dnn_type'},
+          {'name':'DNN engine', 'key':'dnn_engine_name'},
+          {'name':'Model', 'key':'nn_type'},
+          {'name':'Platform', 'key':'plat_name', 'new_line':'yes'},
+          {'name':'CPU', 'key':'cpu_name'},
+          {'name':'OS', 'key':'os_name', 'new_line':'yes'},
+          {'name':'GPGPU', 'key':'gpgpu_name'}]
+
+replay_clean_vars=['no_compile','host_os','device_id']
+replay_clean_env_vars=['CK_CAFFE_MODEL','CK_CAFFE_MODEL_FILE','CK_ENV_MODEL_CAFFE_WEIGHTS']
+  
+##############################################################################
+# Initialize module
+
+def init(i):
+    """
+
+    Input:  {}
+
+    Output: {
+              return       - return code =  0, if successful
+                                         >  0, if error
+              (error)      - error text if return > 0
+            }
+
+    """
+    return {'return':0}
+
+##############################################################################
+# crowdsource these experiments
+
+def crowdsource(i):
+    """
+    Input:  {
[…]

### 2018-01-19 dissemination.publication/request-overview-arxiv/paper.tex
clean up for ArXiv

--- 2018-01-18 dissemination.publication/request-overview-sysml2018/paper.tex
@@
 
-\special{papersize=8.3in,11.7in} % A4
+%\special{papersize=8.3in,11.7in} % A4
 
@@
 conferences. The first ReQuEST workshop will be co-located
-with ASPLOS in March 2018. The workshop will aim to present
+with ASPLOS in March 2018 (ACM conference on Architectural Support for Programming Languages and Operating Systems 
+- the premier forum for multidisciplinary systems research spanning computer architecture 
+and hardware, programming languages and compilers, operating systems and networking).
+The workshop will aim to present
 artifacts submitted by participants, along with

### 2018-01-19 dissemination.publication/request-overview-arxiv/paper_abstract.tex
clean up for ArXiv

--- 2018-01-18 dissemination.publication/request-overview-sysml2018/paper_abstract.tex
@@
 for emerging workloads such as deep learning, starting with ASPLOS'18
+(ACM conference on Architectural Support for Programming Languages and Operating Systems 
+- the premier forum for multidisciplinary systems research spanning computer architecture 
+and hardware, programming languages and compilers, operating systems and networking)
 to build a public repository of the most efficient algorithms and systems

### 2018-02-02 wfe/request/request-template.tex
rewritten ReQuEST CFP +  updated template

@@
-% LaTeX template for Artifact Evaluation V20170622
+% LaTeX template for Artifact Evaluation V20180201
 %
-% Prepared by Grigori Fursin (cTuning foundation, France and dividiti, UK),
-% Bruce Childers (University of Pittsburgh, USA),
-% Thierry Moreau (University of Washington, USA)
+% Prepared by Grigori Fursin (cTuning foundation, France and dividiti, UK)
+% and Thierry Moreau (University of Washington, USA)
+%
+% This document was derived from the original Artifact Appendix
+% prepared by Grigori Fursin (cTuning foundation, France and dividiti, UK) 
+% and Bruce Childers (University of Pittsburgh, USA)
 %
@@
 %
-% (C)opyright 2014-2017
+% (C)opyright 2014-2018
 %
@@
 \begin{abstract}
-Summary of work, and artifact.
+Summary of work and associated workflow artifact.
+
+Please, specify if you want a public or a private evaluation.
 \end{abstract}
@@
 \subsection{Technical Description}
-{\em Obligatory. Provide a technical desciption of your novel work, or references to
-your already published work which you are providing an artifact for.}
+{\em Obligatory. Provide a technical description of your novel work, 
+or references to your already published work which you are providing an artifact for.}
 
@@
 \appendix
-\section{Artifact appendix}
+\section{Artifact Appendix}
 
-Submission and reviewing guidelines and methodology: \\
-{\em http://cTuning.org/ae/submission.html}
+Submission and reviewing methodology: \\
+{\em http://cTuning.org/ae/submission-20171101.html}
 
@@
   \item {\bf Experiments: }
-  \item {\bf Workflow frameworks used?: }
+  \item {\bf Collective Knowledge workflow framework used?: } 
   \item {\bf Publicly available?: }
-\end{itemize}
-
-{\em Obligatory. Provide brief assessment of your artifacts 
-based on {\em https://www.acm.org/publications/policies/artifact-review-badging}}:
-
-\begin{itemize}
-  \item {\bf Artifacts publicly available?: }
-  \item {\bf Artifacts functional?:}
-  \item {\bf Artifacts reusable?:}
-  \item {\bf Results validated?:}
 \end{itemize}
@@
 
-\subsubsection{How delivered}
+\subsubsection{How to obtain?}
 
@@
 
+Please, specify which metrics you improve
+(execution time, accuracy, power consumption, 
+memory usage, device cost, usage cost, etc)
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% When adding this appendix to your paper, 
-% please remove below part
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \end{document}

### 2018-02-03 wfe/request/request-template.tex
Update artifact template.

@@
 %
-% See example of this Artifact Appendix in the CGO'17 paper (with the CK workflow framework):
+% See an example of this Artifact Appendix in the following CGO 2017 paper
+% (with the artifact prepared using the Collective Knowledge framework):
 % https://www.cl.cam.ac.uk/~sa614/papers/Software-Prefetching-CGO2017.pdf
@@
 \begin{abstract}
-Summary of work and associated workflow artifact.
+Please provide a summary of work and associated workflow artifact.
 
-Please, specify if you want a public or a private evaluation.
+Please specify if you would like a public or private evaluation.
 \end{abstract}
@@
 \subsection{Technical Description}
-{\em Obligatory. Provide a technical description of your novel work, 
+{\em Obligatory. Provide a technical description of your new work, 
 or references to your already published work which you are providing an artifact for.}
@@
 
-{\em Obligatory. Use just a few informal keywords in all fields applicable to your artifacts
+{\em Obligatory. Use a few informal keywords in all the fields applicable to your artifacts
 and remove the rest. This information is needed to find appropriate reviewers and gradually 
@@
 
-Please, specify which metrics you improve
+Please specify which metrics you improve
 (execution time, accuracy, power consumption, 
-memory usage, device cost, usage cost, etc)
+memory usage, device cost, usage cost, etc.)
 

### 2018-02-19 module/request.asplos18/module.py
* added specialized module for ASPLOS'18 * started preparing dashboard to visualize results * fixed a few typos

@@ -1,0 +1,1037 @@
+#
+# Collective Knowledge: CK-powered AI/SW/HW co-design for ReQuEST tournaments
+#
+# See CK LICENSE.txt for licensing details
+# See CK COPYRIGHT.txt for copyright details
+#
+# Developer: Grigori Fursin, cTuning foundation/dividiti
+#
+
+cfg={}  # Will be updated by CK (meta description of this module)
+work={} # Will be updated by CK (temporal data)
+ck=None # Will be updated by CK (initialized CK kernel) 
+
+# Local settings
+line='================================================================'
+
+experiment_tags='request-asplos18'
+experiment_repos=['local','ck-request','ck-request-asplos18-results']
+
+form_name='request_web_form'
+onchange='document.'+form_name+'.submit();'
+
+hextra='<center>\n'
+hextra+=' Results from <a href="http://cknowledge.org/request-cfp-asplos2018.html">open ReQuEST @ ASPLOS\'18 tournament</a>\n'
+hextra+='</center>\n'
+hextra+='<p>\n'
+
+selector=[
+          {'name':'Species', 'key':'species'},
+          {'name':'Type', 'key':'prog_type'},
+          {'name':'Test', 'key':'prog_uoa'},
+          {'name':'Dataset', 'key':'dataset_uoa'},
+          {'name':'Platform', 'key':'plat_name', 'new_line':'yes'},
+          {'name':'Time stamp', 'key':'timestamp'}
+         ]
+
+selector2=[
+           {'name':'OpenCL driver', 'key':'##features#gpgpu@0#gpgpu_misc#opencl c version#min', 'skip_empty':'yes', 
+                              'extra_key':'##features#gpgpu@0#gpgpu_misc#opencl_c_version#min'},
+           {'name':'Dataset file', 'key':'##choices#env#CK_DATASET_FILENAME#min', 'new_line':'yes'},
+           {'name':'Batch size', 'key':"##choices#env#CK_IN_SHAPE_N#min", 'type':'int'},
+          ]
+
+selector3=[
+           {'name':'Plot time in', 'key':'plot_time_in'}
+          ]
+
+wchoices3={
+            'plot_time_in':[
+              {'name':'sec', 'value':'sec'},
+              {'name':'ms', 'value':'ms'}
+            ]}
+
+k_hi_uid='highlight_behavior_uid'
[…]

### 2018-02-19 module/request.asplos18/module.py
clean up

@@ -21,6 +21,7 @@ form_name='request_web_form'
 onchange='document.'+form_name+'.submit();'
 
 hextra='<center>\n'
+hextra+='<p>\n'
 hextra+=' Results from <a href="http://cknowledge.org/request-cfp-asplos2018.html">open ReQuEST @ ASPLOS\'18 tournament</a>\n'
 hextra+='</center>\n'
 hextra+='<p>\n'

### 2018-02-20 module/request.asplos18/module.py
added common meta preparation for ReQuEST experiments

@@ -1036,3 +1036,63 @@ def dashboard(i):
     i['cid']=''
 
     return ck.access(i)
+
+##############################################################################
+# prepare common meta for ReQuEST @ ASPLOS"18
+
+def prepare_common_meta(i):
+    """
+    Input:  {
+              platform_dict - output from platform detection
+              request_dict  - info about ReQuEST submission
+            }
+
+    Output: {
+              return       - return code =  0, if successful
+                                         >  0, if error
+              (error)      - error text if return > 0
+
+              tags        - tags for experiment entry
+              meta        - meta for experiment entry
+              record_dict - dict to update records
+            }
+
+    """
+
+    from time import strftime, gmtime
+    import copy
+
+    # Get current timestamp
+    r=ck.get_current_date_time({})
+    if r['return']>0: return r
+    timestamp=r['iso_datetime']
+
+    #striped timestamp
+    j=timestamp.find('.')
+    if j>0: timestamp=timestamp[:j]
+
+    stimestamp=timestamp.replace('-','').replace(':','').replace('T','')
+
+    pd=i['platform_dict']
+    rd=i['request_dict']
+
+    tags=[
+      'request',
+      'request-asplos18',
+      timestamp,
+      stimestamp
+    ]
+
+    meta=copy.deepcopy(rd)
+
+    tags.append(meta['algorithm_species'])
+
+    rd={
+         'subview_uoa':'f84ca49f79a1446a'  # ReQuEST default table view from ck-autotuning repo
+                                           # ck-autotuning:experiment.view:request-default
+       }
+
+
+
+
+    return {'return':0, 'tags':tags, 'meta':meta, 'record_dict':rd}

### 2018-02-20 module/request.asplos18/module.py
improving meta

@@ -1045,6 +1045,7 @@ def prepare_common_meta(i):
     Input:  {
               platform_dict - output from platform detection
               request_dict  - info about ReQuEST submission
+              deps          - resolved deps to summarize deps (package, tags, version)
             }
 
     Output: {
@@ -1073,9 +1074,10 @@ def prepare_common_meta(i):
 
     stimestamp=timestamp.replace('-','').replace(':','').replace('T','')
 
-    pd=i['platform_dict']
+    pi=i['platform_dict']
     rd=i['request_dict']
 
+    # Prepare tags
     tags=[
       'request',
       'request-asplos18',
@@ -1083,16 +1085,96 @@ def prepare_common_meta(i):
       stimestamp
     ]
 
+    tags.append(rd['algorithm_species'])
+
+    # Prepare meta
     meta=copy.deepcopy(rd)
 
-    tags.append(meta['algorithm_species'])
+    meta['timestamp']=timestamp
+    meta['stimestamp']=stimestamp
 
+    meta['request_version']=1
+
+    # Check platform
+    hos=pi['host_os_uoa']
+    hos_uid=pi['host_os_uid']
+    hosd=pi['host_os_dict']
+
+    tos=pi['os_uoa']
+    tos_uid=pi['os_uid']
+    tosd=pi['os_dict']
+    tbits=tosd.get('bits','')
+
+    remote=tosd.get('remote','')
+
+    tdid=pi['device_id']
+
+    features=pi.get('features',{})
+
+    fplat=features.get('platform',{})
+    fos=features.get('os',{})
+    fcpu=features.get('cpu',{})
+
+    plat_name=fplat.get('name','')
+    plat_uid=features.get('platform_uid','')
+    os_name=fos.get('name','')
+    os_uid=features.get('os_uid','')
+    cpu_name=fcpu.get('name','')
+    cpu_abi=fcpu.get('cpu_abi','')
+    if cpu_name=='' and cpu_abi!='': cpu_name='unknown-'+cpu_abi
+    cpu_uid=features.get('cpu_uid','')
+    sn=fos.get('serial_number','')
+
+    # Check if CPU clusters (TBD: need to know which one is actually used!)
+    if cpu_name=='':
+       ufcpu=features.get('cpu_unique',[])
+       if len(ufcpu)>1:
+           for q in ufcpu:
+               if cpu_name!='': cpu_name+=' ; '
+               x=q.get('ck_cpu_name','')
[…]

### 2018-02-20 module/request.asplos18/module.py
added resursive deps summary!

@@ -1076,6 +1076,7 @@ def prepare_common_meta(i):
 
     pi=i['platform_dict']
     rd=i['request_dict']
+    deps=i.get('deps',{})
 
     # Prepare tags
     tags=[
@@ -1170,6 +1171,15 @@ def prepare_common_meta(i):
                  'gpgpu_vendor':gpgpu_vendor,
                  'opencl':opencl
                 })
+
+    # Process dependencies
+    r=ck.access({'action':'deps_summary',
+                 'module_uoa':cfg['module_deps']['env'],
+                 'deps':deps})
+    if r['return']>0: return r
+    deps_summary=r['deps_summary']
+
+    meta['deps_summary']=deps_summary
 
     # Misc info
     rd={

### 2018-02-20 module/request.asplos18/module.py
fixed opencl detection

@@ -1147,7 +1147,7 @@ def prepare_common_meta(i):
     gpgpu_name2=gpgpu_name
     if gpgpu_vendor!='': gpgpu_name2=gpgpu_vendor+' '+gpgpu_name
 
-    fgpgpu_misc=features.get('gpgpu_misc',{})
+    fgpgpu_misc=features.get('gpgpu',{}).get('gpgpu_misc',{})
     opencl=fgpgpu_misc.get('opencl c version','')
 
     # Assembling meta for platform

### 2018-06-09 dissemination.publication/request-asplos18-front-matter/paper.tex
preparing proceedings front matter

%% For ACM ADAPT DL proceedings %%
\documentclass[10pt,onecolumn]{article}

\usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{float}
\usepackage{enumerate}
\usepackage{url}
\usepackage{hyperref}

\newenvironment{packed_itemize}{
\begin{itemize}
  \setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}
}{\end{itemize}}

\date{}

\begin{document}

\title{Introducing 1\textsuperscript{st} ACM SIGARCH ReQuEST Workshop/Tournament \\
on Reproducible Software/Hardware Co-design \\
of Pareto-Efficient Image Classification\\[.5cm]
\textbf{\href{http://cKnowledge.org/request-cfp-asplos2018.html}{cKnowledge.org/request-cfp-asplos2018.html}}
\textbf{\href{http://cKnowledge.org/request}{cKnowledge.org/request}}
}

\author{}

\maketitle
\thispagestyle{empty}
\pagestyle{empty}

\begin{center}
co-located with ACM ASPLOS 2018 (Williamsburg, VA, USA) \\
March 24th, 2018 \\
(proposal submitted in June 2017)
\end{center}

\textbf{Organizers (A-Z):}

\begin{packed_itemize}

 \item Luis Ceze, University of Washington, USA
 \item Natalie Enright Jerger, University of Toronto, Canada
 \item Babak Falsafi, EPFL, Switzerland
 \item \textit{Grigori Fursin, cTuning foundation, France (reproducibility and common workflow framework)}
 \item \textit{Anton Lokhmotov, dividiti, UK (industrial relations)}
 \item \textit{Thierry Moreau, University of Washington, USA (workshop organization)}
 \item Adrian Sampson, Cornell University, USA
 \item Phillip Stanley Marbell, University of Cambridge, UK

\end{packed_itemize}

\textbf{Advisory board (A-Z):}

\begin{packed_itemize}

 \item Michaela Blott, Xilinx
 \item Unmesh Bordoloi, General Motors
 \item Ofer Dekel, Microsoft
 \item Maria Girone, CERN openlab
 \item Wayne Graves, ACM
 \item Vinod Grover, NVIDIA
 \item Sumit Gupta, IBM
 \item James Hetherington, Alan Turing Institute
 \item Steve Keckler, NVIDIA
 \item Wei Li, Intel
 \item Colin Osborne, ARM
 \item Andrew Putnam, Microsoft
 \item Boris Shulkin, Magna
 \item Greg Stoner, AMD
 \item Alex Wade, Chan Zuckerberg Initiative
 \item Peng Wu, Huawei
 \item Cliff Young, Google

\end{packed_itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage

\section*{Introduction}
\label{sec:intro}

\begin{figure*}[ht]
  \centering
  \includegraphics[width=0.9\textwidth]{figures/ck-request-concept-cropped.pdf}
  \caption{Reproducible ACM ReQuEST tournaments involving interdisciplinary community
  to decompose complex software/hardware benchmarking,
  optimization and co-design process into customizable
  Collective Knowledge workflows with reusable components, and collaboratively
  explore Pareto-efficient solutions in terms of speed,
  accuracy, energy, costs and other extensible metrics
  across diverse models, data sets, frameworks, libraries and platforms.}
  \label{fig:ck-request-concept}
\end{figure*}

\end{document}

### 2018-06-09 report/request-asplos18-front-matter/_generate_interactive_ck_article.sh

@@ -1,0 +1,2 @@
+# generate bbl in the format understandable by CK
+ck convert_to_live_ck_report dissemination.publication:request-asplos18-front-matter --output=interactive-ck-article.html

### 2018-06-09 report/request-asplos18-report/_generate_interactive_ck_article.sh

@@ -1,2 +1,0 @@
-# generate bbl in the format understandable by CK
-ck convert_to_live_ck_report dissemination.publication:request-asplos18-report --output=interactive-ck-article.html

### 2018-06-12 dissemination.publication/request-asplos18-front-matter/paper.tex
updated front matter

@@
 
-\title{Introducing 1\textsuperscript{st} ACM SIGARCH ReQuEST Workshop/Tournament \\
+\title{Introducing the 1\textsuperscript{st} ACM ReQuEST Workshop/Tournament \\
 on Reproducible Software/Hardware Co-design \\
-of Pareto-Efficient Image Classification\\[.5cm]
+of Pareto-Efficient Deep Learning\\[.5cm]
 \textbf{\href{http://cKnowledge.org/request-cfp-asplos2018.html}{cKnowledge.org/request-cfp-asplos2018.html}}
@@
 
-\textbf{Organizers (A-Z):}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section*{Overview}
+\label{sec:overview}
+
+Artificial Intelligence (AI), Machine Learning (ML) and other
+emerging workloads demand efficient computer systems from the
+cloud to the edge. Systems designers, however, face numerous
+challenges from tackling the ever-growing space of design and
+optimization choices (including algorithms, models, software
+frameworks, libraries, hardware platforms, optimization
+techniques) to balancing off multiple objectives (including
+accuracy, speed, throughput, power, size, price). Furthermore,
+the lack of a common experimental framework and methodology
+makes it even more challenging to keep up with and build upon
+the latest research advances.
+
+The ACM Reproducible Quality-Efficient Systems Tournaments
+initiative (\href{http://cKnowledge.org/request}{ReQuEST}) 
+invites a multidisciplinary community
+(workloads/software/hardware) to decompose the complex
+multi-objective benchmarking, co-design and optimization
+process into customizable workflows with \href{https://github.com/ctuning/ck/wiki#user-content-reusable-ck-components}{reusable components}
+(see the \href{https://arxiv.org/abs/1801.06378}{introduction} to ReQuEST). We leverage the open
+Collective Knowledge workflow framework (\href{https://github.com/ctuning/ck}{CK}) 
+and the rigorous \href{http://cTuning.org/ae}{ACM artifact evaluation methodology (AE)} to allow the
+community collaboratively explore quality vs. efficiency
+trade-offs for rapidly evolving workloads across diverse
+systems.
+
+The \href{http://cknowledge.org/request-cfp-asplos2018.html}{1st ReQuEST tournament} 
+served as a proof-of-concept of our approach. We invited the community to submit complete
+implementations (code, data, scripts, etc.) for the popular
+\href{http://www.image-net.org}{ImageNet} object classification challenge. For several weeks,
+four volunteers collaborated with the authors to convert their
+artifacts into a common CK format and evaluate the converted
+artifacts on the original or similar platforms. The evaluation
+metrics included accuracy on the ImageNet validation set
+(50,000 images), latency (seconds per image), throughput
+(images per second), platform price (dollars) and peak power
+consumption (Watts).
+
+Since collapsing all metrics into one to select a single
+winner often results in over-engineered solutions, we have
+opted instead to select multiple implementations from
+a Pareto-frontier, based on their uniqueness or simply
+to obtain a reference implementation. The authors of such
+selected solutions were given an opportunity to share their
+insights at the associated \href{http://cknowledge.org/request-cfp-asplos2018.html}{ReQuEST workshop} 
+co-located with the 23rd ACM ASPLOS conference at the end of March 2018
+in Williamsburg, VA, USA.
+
+\begin{center}
+\includegraphics[width=0.9\textwidth]{figures/ck-request-concept-cropped.pdf}
+\end{center}
+
+The ReQuEST-ASPLOS'18 proceedings, available in the 
+\href{https://dl.acm.org}{ACM Digital Library}, include five papers with Artifact Appendices
+and a set of \href{https://www.acm.org/publications/policies/artifact-review-badging}{ACM reproducibility badges}. 
+The proceedings are accompanied by snapshots of Collective Knowledge workflows
+covering a very diverse model/software/hardware stack:
+
+\begin{packed_itemize}
+
+ \item \textbf{Models:} MobileNets, ResNet-18, ResNet-50, Inception-v3, VGG16, AlexNet, SSD.
+ \item \textbf{Data types:} 8-bit integer, 16-bit floating-point (half), 32-bit floating-point (float).
+ \item \textbf{AI frameworks and libraries:} MXNet, TensorFlow, Caffe, Keras, Arm Compute Library, cuDNN, TVM, NNVM.
+ \item \textbf{Platforms:} Xilinx Pynq-Z1 FPGA, Arm Cortex CPUs and Arm Mali GPGPUs (Linaro HiKey960 and T-Firefly RK3399), a farm of Raspberry Pi devices, NVIDIA Jetson TX1 and TX2, and Intel Xeon servers in Amazon Web Services, Google Cloud and Microsoft Azure.
+
+\end{packed_itemize}
+
+The validated ReQuEST-ASPLOS'18 \href{http://github.com/ctuning/ck-request-asplos18-results}{results}, 
+available on the \href{http://cKnowledge.org/request-results}{ReQuEST scoreboard}, also exhibit amazing diversity:
+
+\begin{packed_itemize}
+
+ \item \textbf{Latency:} 4 .. 500 milliseconds per image
+ \item \textbf{Throughput:} 2 .. 465 images per second
+ \item \textbf{Top 1 accuracy:} 41 .. 75 percent
+ \item \textbf{Top 5 accuracy:} 65 .. 93 percent
+ \item \textbf{Model size (pre-trained weights):} 2 .. 130 megabytes
+ \item \textbf{Peak power consumption:} 2.5 .. 180 Watts
+ \item \textbf{Device frequency:} 100 .. 2600 megahertz
+ \item \textbf{Device cost:} 40 .. 1200 dollars
+ \item \textbf{Cloud usage cost:} 2.6E-6 .. 9.5E-6 dollars per inference
+
+\end{packed_itemize}
+
+Most importantly, the community can now access all the above
+CK workflows under permissive licenses and continue
+collaborating on them via dedicated 
+\href{https://github.com/ctuning/ck-request-asplos18-results}{ReQuEST'18 GitHub projects}. 
+First, the workflows can be automatically \href{https://github.com/ctuning/ck/wiki/Portable-workflows}{adapted}
+to new platforms and environments by either detecting already
+installed dependencies (e.g. libraries) or rebuilding
+dependencies via an integrated \href{http://cKnowledge.org/shared-packages.html}{package manager} supporting
+Linux, Windows, MacOS and Android. Second, the workflows can
+be customized by swapping in new models, data sets,
+frameworks, libraries, and so on. Third, the workflows can be
+extended to expose new design and optimization choices (e.g.
+quantization), as well as evaluation metrics (e.g. power
+or memory consumption). Finally, the workflows can be used for
+collaborative autotuning ("\href{http://cKnowledge.org/rpi-crowd-tuning}{crowd-tuning}") 
+to explore huge optimization spaces using devices such as 
+\href{https://play.google.com/store/apps/details?id=openscience.crowdsource.video.experiments}{Android phones and tablets}, 
+with best solutions being made available to the
+community on the \href{http://cKnowledge.org/dnn-crowd-benchmarking-results}{online CK scoreboard}.
+
+Our overwhelmingly positive experience has also allowed us to
+critically assess several potential issues with scaling
+up this approach and suggest how to overcome them:
+
+\begin{packed_itemize}
+
+ \item
+
+Fair competitive benchmarking between different platforms,
+frameworks and models is hard work. It requires carefully
+considering model equivalence (e.g. performing the same mix of
+operations), input equivalence (e.g. preprocessing the inputs
+in the same way), output equivalence (e.g. validating the
+outputs for each input, not just calculating the usual
+aggregate accuracy score), etc. Formalizing the benchmarking
+requirements and encapsulating them in shared CK components
+(e.g. using a framework-independent model representation such
+as \href{https://onnx.ai/}{ONNX}) and workflows (e.g. for input conversion and output
+validation), should help standardize and automate the
+benchmarking process.
+
+ \item
+
+Thorough artifact evaluation can take several person-weeks.
+Each submitted workflow needs to be studied in detail in its
+original form and then converted into a common format.
+However, the more reusable CK components (such as 
+\href{http://cKnowledge.org/shared-programs.html}{workflows},
+\href{http://cKnowledge.org/shared-modules.html}{modules/plugins}, 
+\href{http://cKnowledge.org/shared-packages.html}{packages}) 
+are shared by the community, the easier the conversion becomes. 
+For example, we have
+successfully reused several previously 
+\href{https://github.com/ctuning/ck/wiki#user-content-reusable-ck-components}{shared components} 
+for models, frameworks and libraries, as well as the universal
+CK workflow for \href{http://cKnowledge.org/rpi-crowd-tuning}{program benchmarking and autotuning}.
+We propose to introduce a new 
+\href{https://www.acm.org/publications/policies/artifact-review-badging}{ACM reproducibility badge} 
+for such unified "plug\&play" components. This could eventually
+lead to creating a "marketplace" for Pareto-efficient
+implementations (code and data) shared as portable,
+customizable and reusable CK components.
+
+\begin{center}\includegraphics{ck-assets/artifacts_automated_dl.jpg}\end{center}
+
+ \item
+
+Artifact evaluation may require access to expensive
+computational resources (e.g. cloud instances with 72-core
+servers), proprietary tools (e.g. Intel compilers), and
+auxiliary hardware (e.g. power meters). Raising the profile
+of AE by widely recognizing its benefits and impact should
+help us obtain access, licensees and sponsorship from the
+industry and funding agencies.
+
+ \item
+
+Full experimental evaluation can take many weeks (for example,
+when validating accuracy on 50,000 images on a 100 MHz FPGA
+board). The AE committee can collaborate with the authors
+to determine a minimally useful scope for evaluation which
+would still provide insights to the community. The community
+can eventually crowdsource full evaluation. In other words,
+AE can be "staged" with a quick check that the artifacts are
+"functional" before the camera-ready deadline followed by full
+evaluation using the ReQuEST methodology. In fact, ReQuEST can
+grow into a non-profit service to conferences and journals.
+Sponsorship should help attract experienced full-time
+evaluators, as well as part-time volunteers to work
+on unifying and evaluating artifacts and workflows.
+
+\end{packed_itemize}
+
+Our future plans include:
+
+\begin{packed_itemize}
+
+\item collaborating with the community, our Advisory Board and ACM to address the above issues;
+\item using the ReQuEST experience to assist AE at the upcoming \href{http://sysml.cc}{SysML'19} conference;
+\item replacing non-representative benchmarks with realistic workloads;
+\item creating realistic training sets based on mispredictions shared by the community;
+\item improving the benchmarking and co-design methodology, and contributing to emerging benchmarking initiatives such as \href{http://mlperf.org}{MLPerf};
+\item collaborating with other competitions such as \href{https://rebootingcomputing.ieee.org/lpirc}{LPIRC}, \href{https://dawn.cs.stanford.edu/benchmark}{DAWNBench} and \href{https://sc18.supercomputing.org/experience/studentssc/student-cluster-competition}{SCC} on developing a common experimental framework;
+\item standardizing \href{http://cKnowledge.org/rpi-crowd-tuning}{multi-objective autotuning and co-design workflows};
+\item improving and documenting the experimental framework and scoreboard;
+\item generating reproducible and interactive reports (see examples \href{http://cknowledge.org/repo/web.php?wcid=report:request-overview}{1} and \href{http://cKnowledge.org/rpi-crowd-tuning}{2});
+\item adding new shared components such as workloads, data sets, tools and platforms;
+\item automating AE "at the source" by integrating CK workflows with e.g. \href{https://hotcrp.com/}{HotCRP};
+\item standardizing APIs and meta-descriptions of shared components to make them "marketplace-ready";
+\item running new ReQuEST competitions for other workloads!
+
+\end{packed_itemize}
+
+We are also organizing a related \href{http://rescue-hpc.org}{ResCuE-HPC workshop}
+at \href{https://sc18.supercomputing.org/}{Supercomputing'18} to discuss with the community some of the
+above issues focusing on how to develop reproducible,
+customizable and portable workflows for high-performance
+computing (HPC).
+
+Our long-term vision is to dramatically reduce the complexity
+and costs of the development and deployment of AI, ML and
+other emerging workloads. We believe that having an open
+repository (marketplace) of customizable workflows with
+reusable components helps to bring together the
+multidisciplinary community to collaboratively co-design,
+optimize and autotune computer systems across the full
+model/software/hardware stack. Systems integrators will also
+benefit from being able to assemble complete solutions
+by adapting such reusable components to their specific usage
+scenarios, requirements and constraints. We envision that our
+community-driven approach and decentralized marketplace will
+help accelerate adoption and technology transfer of novel
+AI/ML techniques similar to the open-source movement.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection*{Acknowledgments}
+
+We thank the ReQuEST Advisory Board for their enthusiastic
+support of our vision; the ReQuEST authors for being very
+responsive when converting their workflows to the CK format
+and during artifact evaluation; Flavio Vella and Nikolai
+Chunosov for their help with unifying and evaluating
+submissions; Xipeng Shen and James Tuck for their support for
+organizing the ReQuEST workshop at ASPLOS'18; Craig Rodkin,
+Asad Ali and Wayne Graves for helping to prepare the ACM DL
+proceedings with CK workflows, and the CK community for their
+contributions.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section*{Organizers (A-Z)}
 
@@
 
-\textbf{Advisory board (A-Z):}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section*{Advisory board (A-Z)}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
+\section*{Table of contents}
+\label{sec:overview}
 
-\section*{Introduction}
-\label{sec:intro}
-
-\begin{figure*}[ht]
-  \centering
-  \includegraphics[width=0.9\textwidth]{figures/ck-request-concept-cropped.pdf}
-  \caption{Reproducible ACM ReQuEST tournaments involving interdisciplinary community
-  to decompose complex software/hardware benchmarking,
-  optimization and co-design process into customizable
-  Collective Knowledge workflows with reusable components, and collaboratively
-  explore Pareto-efficient solutions in terms of speed,
-  accuracy, energy, costs and other extensible metrics
-  across diverse models, data sets, frameworks, libraries and platforms.}
-  \label{fig:ck-request-concept}
-\end{figure*}
+\begin{tabular}{|p{2.85in}|p{0.52in}|p{0.62in}|p{0.56in}|p{0.69in}|p{0.63in}|}
+\hline\hline
+  \begin{center}\small\textbf{Paper}\end{center} &   \begin{center}\small\textbf{Artifact\newline available}\end{center} &   \begin{center}\small\textbf{Artifact\newline functional}\end{center} &   \begin{center}\small\textbf{Artifact\newline reusable}\end{center} &   \begin{center}\small\textbf{Results\newline reproduced}\end{center} &   \begin{center}\small\textbf{Results\newline replicated}\end{center} \\
+\hline
+  \textbf{Highly Efficient 8-bit Low Precision Inference of Convolutional Neural Networks with IntelCaffe}\newline\newline{Jiong Gong, Haihao Shen, Guoming Zhang, Xiaoli Liu, Shane Li, Ge Jin, Niharika Maheshwari, Evarist Fomenko, Eden Segal}\newline\newline [~\href{https://doi.org/10.1145/3229762.3229763}{Paper DOI}~] [~\href{https://doi.org/10.1145/3229769}{Artifact DOI}~] [~\href{https://github.com/intel/caffe}{Original artifact}~] [~\href{https://github.com/ctuning/ck-request-asplos18-caffe-intel}{CK workflow}~] [~\href{https://github.com/ctuning/ck-request-asplos18-results-caffe-intel}{CK results}~]\newline &  \begin{center}\includegraphics{ck-assets/artifacts_available_dl.jpg}\end{center} &  ~ &  \begin{center}\includegraphics{ck-assets/artifacts_evaluated_reusable_dl.jpg}\end{center} &  ~ &  \begin{center}\includegraphics{ck-assets/results_replicated_dl.jpg}\end{center} \\
+\hline
+  \textbf{Optimizing Deep Learning Workloads on ARM GPU with TVM}\newline\newline{Lianmin Zheng, Tianqi Chen}\newline\newline [~\href{https://doi.org/10.1145/3229762.3229764}{Paper DOI}~] [~\href{https://doi.org/10.1145/3229770}{Artifact DOI}~] [~\href{https://github.com/merrymercy/tvm-mali}{Original artifact}~] [~\href{https://github.com/ctuning/ck-request-asplos18-mobilenets-tvm-arm}{CK workflow}~] [~\href{https://github.com/ctuning/ck-request-asplos18-results-mobilenets-tvm-arm}{CK results}~]\newline &  \begin{center}\includegraphics{ck-assets/artifacts_available_dl.jpg}\end{center} &  ~ &  \begin{center}\includegraphics{ck-assets/artifacts_evaluated_reusable_dl.jpg}\end{center} &  ~ &  \begin{center}\includegraphics{ck-assets/results_replicated_dl.jpg}\end{center} \\
+\hline
+  \textbf{Real-Time Image Recognition Using Collaborative IoT Devices}\newline\newline{Ramyad Hadidi, Jiashen Cao, Matthew Woodward, Michael S.
+Ryoo, Hyesoon Kim}\newline\newline [~\href{https://doi.org/10.1145/3229762.3229765}{Paper DOI}~] [~\href{https://doi.org/10.1145/3229771}{Artifact DOI}~] [~\href{https://github.com/parallel-ml/asplos2018-workshop}{Original artifact}~] [~\href{https://github.com/ctuning/ck-request-asplos18-iot-farm}{CK workflow}~] [~\href{https://github.com/ctuning/ck-request-asplos18-results-iot-farm}{CK results}~]\newline &  \begin{center}\includegraphics{ck-assets/artifacts_available_dl.jpg}\end{center} &  ~ &  \begin{center}\includegraphics{ck-assets/artifacts_evaluated_reusable_dl.jpg}\end{center} &  ~ &  \begin{center}\includegraphics{ck-assets/results_replicated_dl.jpg}\end{center} \\
+\hline
+  \textbf{Leveraging the VTA-TVM Hardware-Software Stack for FPGA Acceleration of 8-bit ResNet-18 Inference}\newline\newline{Thierry Moreau}\newline\newline [~\href{https://doi.org/10.1145/3229762.3229766}{Paper DOI}~] [~\href{https://doi.org/10.1145/3229772}{Artifact DOI}~] [~\href{https://github.com/uwsaml/vta}{Original artifact}~] [~\href{https://github.com/ctuning/ck-request-asplos18-resnet-tvm-fpga}{CK workflow}~] [~\href{https://github.com/ctuning/ck-request-asplos18-results-resnet-tvm-fpga}{CK results}~]\newline &  ~ &  \begin{center}\includegraphics{ck-assets/artifacts_evaluated_functional_dl.jpg}\end{center} &  ~ &  ~ &  \begin{center}\includegraphics{ck-assets/results_replicated_dl.jpg}\end{center} \\
+\hline
+  \textbf{Multi-objective autotuning of MobileNets across the full software/hardware stack}\newline\newline{Anton Lokhmotov, Nikolay Chunosov, Flavio Vella, Grigori Fursin}\newline\newline [~\href{https://doi.org/10.1145/3229762.3229767}{Paper DOI}~] [~\href{https://doi.org/10.1145/3229773}{Artifact DOI}~] [~\href{https://github.com/dividiti/ck-request-asplos18-mobilenets-armcl-opencl}{CK workflow}~] [~\href{https://github.com/ctuning/ck-request-asplos18-results-mobilenets-armcl-opencl}{CK results}~]\newline &  \begin{center}\includegraphics{ck-assets/artifacts_available_dl.jpg}\end{center} &  ~ &  \begin{center}\includegraphics{ck-assets/artifacts_evaluated_reusable_dl.jpg}\end{center} &  ~ &  \begin{center}\includegraphics{ck-assets/results_replicated_dl.jpg}\end{center} \\
+\hline
+\hline
+\end{tabular}
 

### 2018-06-12 dissemination.publication/request-asplos18-front-matter/paper.tex
minor fixes

@@
 a Pareto-frontier, based on their uniqueness or simply
-to obtain a reference implementation. The authors of such
+to obtain a reference implementation. The authors of
 selected solutions were given an opportunity to share their
 insights at the associated \href{http://cknowledge.org/request-cfp-asplos2018.html}{ReQuEST workshop} 
-co-located with the 23rd ACM ASPLOS conference at the end of March 2018
-in Williamsburg, VA, USA.
+co-located with the 23rd ACM ASPLOS conference.
 
@@
 to new platforms and environments by either detecting already
-installed dependencies (e.g. libraries) or rebuilding
+installed dependencies (e.g.\ libraries) or rebuilding
 dependencies via an integrated \href{http://cKnowledge.org/shared-packages.html}{package manager} supporting
@@
 frameworks, libraries, and so on. Third, the workflows can be
-extended to expose new design and optimization choices (e.g.
-quantization), as well as evaluation metrics (e.g. power
+extended to expose new design and optimization choices (e.g.\ quantization), as well as evaluation metrics (e.g. power
 or memory consumption). Finally, the workflows can be used for
@@
 frameworks and models is hard work. It requires carefully
-considering model equivalence (e.g. performing the same mix of
-operations), input equivalence (e.g. preprocessing the inputs
-in the same way), output equivalence (e.g. validating the
+considering model equivalence (e.g.\ performing the same mix of
+operations), input equivalence (e.g.\  preprocessing the inputs
+in the same way), output equivalence (e.g.\ validating the
 outputs for each input, not just calculating the usual
@@
 requirements and encapsulating them in shared CK components
-(e.g. using a framework-independent model representation such
-as \href{https://onnx.ai/}{ONNX}) and workflows (e.g. for input conversion and output
+(e.g.\ using a framework-independent model representation such
+as \href{https://onnx.ai/}{ONNX}) and workflows (e.g.\ for input conversion and output
 validation), should help standardize and automate the
@@
 
-\begin{center}\includegraphics{ck-assets/artifacts_automated_dl.jpg}\end{center}
+%\begin{center}\includegraphics{ck-assets/artifacts_automated_dl.jpg}\end{center}
 
@@
 Artifact evaluation may require access to expensive
-computational resources (e.g. cloud instances with 72-core
+computational resources (e.g.\ cloud instances with 72-core
 servers), proprietary tools (e.g. Intel compilers), and
-auxiliary hardware (e.g. power meters). Raising the profile
+auxiliary hardware (e.g.\ power meters). Raising the profile
 of AE by widely recognizing its benefits and impact should
@@
 Sponsorship should help attract experienced full-time
-evaluators, as well as part-time volunteers to work
+evaluators, as well as part-time volunteers, to work
 on unifying and evaluating artifacts and workflows.
@@
 \item adding new shared components such as workloads, data sets, tools and platforms;
-\item automating AE "at the source" by integrating CK workflows with e.g. \href{https://hotcrp.com/}{HotCRP};
+\item automating AE "at the source" by integrating CK workflows with e.g.\ \href{https://hotcrp.com/}{HotCRP};
 \item standardizing APIs and meta-descriptions of shared components to make them "marketplace-ready";
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{Acknowledgments}
+\section*{Acknowledgments}
 
@@
  \item Wei Li, Intel
- \item Colin Osborne, ARM
+ \item Colin Osborne, Arm
  \item Andrew Putnam, Microsoft
@@
 \hline
-  \textbf{Optimizing Deep Learning Workloads on ARM GPU with TVM}\newline\newline{Lianmin Zheng, Tianqi Chen}\newline\newline [~\href{https://doi.org/10.1145/3229762.3229764}{Paper DOI}~] [~\href{https://doi.org/10.1145/3229770}{Artifact DOI}~] [~\href{https://github.com/merrymercy/tvm-mali}{Original artifact}~] [~\href{https://github.com/ctuning/ck-request-asplos18-mobilenets-tvm-arm}{CK workflow}~] [~\href{https://github.com/ctuning/ck-request-asplos18-results-mobilenets-tvm-arm}{CK results}~]\newline &  \begin{center}\includegraphics{ck-assets/artifacts_available_dl.jpg}\end{center} &  ~ &  \begin{center}\includegraphics{ck-assets/artifacts_evaluated_reusable_dl.jpg}\end{center} &  ~ &  \begin{center}\includegraphics{ck-assets/results_replicated_dl.jpg}\end{center} \\
+  \textbf{Optimizing Deep Learning Workloads on Arm GPU with TVM}\newline\newline{Lianmin Zheng, Tianqi Chen}\newline\newline [~\href{https://doi.org/10.1145/3229762.3229764}{Paper DOI}~] [~\href{https://doi.org/10.1145/3229770}{Artifact DOI}~] [~\href{https://github.com/merrymercy/tvm-mali}{Original artifact}~] [~\href{https://github.com/ctuning/ck-request-asplos18-mobilenets-tvm-arm}{CK workflow}~] [~\href{https://github.com/ctuning/ck-request-asplos18-results-mobilenets-tvm-arm}{CK results}~]\newline &  \begin{center}\includegraphics{ck-assets/artifacts_available_dl.jpg}\end{center} &  ~ &  \begin{center}\includegraphics{ck-assets/artifacts_evaluated_reusable_dl.jpg}\end{center} &  ~ &  \begin{center}\includegraphics{ck-assets/results_replicated_dl.jpg}\end{center} \\
 \hline

### 2018-06-13 dissemination.publication/request-asplos18-front-matter/paper.tex
added one more bullet point
updated TOC

@@
 \item standardizing \href{http://cKnowledge.org/rpi-crowd-tuning}{multi-objective autotuning and co-design workflows};
+\item extending unified collection of platform information in CK;
 \item improving and documenting the experimental framework and scoreboard;
@@
 \hline
-  \textbf{Optimizing Deep Learning Workloads on Arm GPU with TVM}\newline\newline{Lianmin Zheng, Tianqi Chen}\newline\newline [~\href{https://doi.org/10.1145/3229762.3229764}{Paper DOI}~] [~\href{https://doi.org/10.1145/3229770}{Artifact DOI}~] [~\href{https://github.com/merrymercy/tvm-mali}{Original artifact}~] [~\href{https://github.com/ctuning/ck-request-asplos18-mobilenets-tvm-arm}{CK workflow}~] [~\href{https://github.com/ctuning/ck-request-asplos18-results-mobilenets-tvm-arm}{CK results}~]\newline &  \begin{center}\includegraphics{ck-assets/artifacts_available_dl.jpg}\end{center} &  ~ &  \begin{center}\includegraphics{ck-assets/artifacts_evaluated_reusable_dl.jpg}\end{center} &  ~ &  \begin{center}\includegraphics{ck-assets/results_replicated_dl.jpg}\end{center} \\
+  \textbf{Optimizing Deep Learning Workloads on ARM GPU with TVM}\newline\newline{Lianmin Zheng, Tianqi Chen}\newline\newline [~\href{https://doi.org/10.1145/3229762.3229764}{Paper DOI}~] [~\href{https://doi.org/10.1145/3229770}{Artifact DOI}~] [~\href{https://github.com/merrymercy/tvm-mali}{Original artifact}~] [~\href{https://github.com/ctuning/ck-request-asplos18-mobilenets-tvm-arm}{CK workflow}~] [~\href{https://github.com/ctuning/ck-request-asplos18-results-mobilenets-tvm-arm}{CK results}~]\newline &  \begin{center}\includegraphics{ck-assets/artifacts_available_dl.jpg}\end{center} &  ~ &  \begin{center}\includegraphics{ck-assets/artifacts_evaluated_reusable_dl.jpg}\end{center} &  ~ &  \begin{center}\includegraphics{ck-assets/results_replicated_dl.jpg}\end{center} \\
 \hline
@@
 \hline
-  \textbf{Leveraging the VTA-TVM Hardware-Software Stack for FPGA Acceleration of 8-bit ResNet-18 Inference}\newline\newline{Thierry Moreau}\newline\newline [~\href{https://doi.org/10.1145/3229762.3229766}{Paper DOI}~] [~\href{https://doi.org/10.1145/3229772}{Artifact DOI}~] [~\href{https://github.com/uwsaml/vta}{Original artifact}~] [~\href{https://github.com/ctuning/ck-request-asplos18-resnet-tvm-fpga}{CK workflow}~] [~\href{https://github.com/ctuning/ck-request-asplos18-results-resnet-tvm-fpga}{CK results}~]\newline &  ~ &  \begin{center}\includegraphics{ck-assets/artifacts_evaluated_functional_dl.jpg}\end{center} &  ~ &  ~ &  \begin{center}\includegraphics{ck-assets/results_replicated_dl.jpg}\end{center} \\
+  \textbf{Leveraging the VTA-TVM Hardware-Software Stack for FPGA Acceleration of 8-bit ResNet-18 Inference}\newline\newline{Thierry Moreau, Tianqi Chen, Luis Ceze}\newline\newline [~\href{https://doi.org/10.1145/3229762.3229766}{Paper DOI}~] [~\href{https://doi.org/10.1145/3229772}{Artifact DOI}~] [~\href{https://github.com/uwsaml/vta}{Original artifact}~] [~\href{https://github.com/ctuning/ck-request-asplos18-resnet-tvm-fpga}{CK workflow}~] [~\href{https://github.com/ctuning/ck-request-asplos18-results-resnet-tvm-fpga}{CK results}~]\newline &  ~ &  \begin{center}\includegraphics{ck-assets/artifacts_evaluated_functional_dl.jpg}\end{center} &  ~ &  ~ &  \begin{center}\includegraphics{ck-assets/results_replicated_dl.jpg}\end{center} \\
 \hline

### 2018-06-14 report/request-asplos18-front-matter/_generate_interactive_ck_article.sh
improving description and removing unused parts

@@ -1,2 +1,0 @@
-# generate bbl in the format understandable by CK
-ck convert_to_live_ck_report dissemination.publication:request-asplos18-front-matter --output=interactive-ck-article.html
